\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
my attempt at a slightly better introduction to gdml2fluka section.
describe what a region is as soon as we refer to it.  (slight reordering)

rewording of the description of a region so that we mention zones, which I
think are important, and a more top-down description, starting with the
definition of a region, then to a zone, and then explaining the zone in
terms of primtives.

\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
solids can be mapped to a FLUKA region. Some solids in Geant4 directly map to 
a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
A region is a region of space which is formed of bodies and the operators $+$ (intersection), $-$ 
(complement) and $\:|\:$ (union), also parentheses to indicate the order of operations. FLUKA 
has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
plane (PLA), Z-axis aligned cylinder (ZCC), Z-axis aligned elliptical cylinder (ZEC), 
sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
\begin{figure}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
\caption{Example conversion of a simple GDML geometry to FLUKA, above:
the original model in \PYGEOMETRY{}, below: the converted FLUKA geometry
viewed in flair. The example is a sector bend dipole electromagnet.}
\label{fig:gdml-flair}
\end{center}
\end{figure}

>>>>

\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each
of the Geant4 solids can be mapped to a FLUKA region.  A region is a region
of space defined by a material and the Boolean disjunction (a union using
the operator~$\:|\:$ in free format geometry) of one or more
zones. Each zone is then defined in terms of the conjunction (intersection
with~$+$, subtraction with~$-$) of one or more primitive bodies, as well as
parentheses to determine the order of operations within the zone.  FLUKA
has 20 of these primitive bodies, listed in Table~\ref{tab:Fluka2Geant4}
and, in general, infinite extent bodies have tracking accuracy and
efficiency benefits over finite ones. Key for conversion are XY-, XZ-,
YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), Z-axis aligned cylinder
(ZCC), Z-axis aligned elliptical cylinder (ZEC), sphere (SPH), truncated
right-angle cone (TRC) and general quadric surface (QUA). Some solids in
Geant4 directly map to a single FLUKA body, others require the construction
of a simple FLUKA CSG tree combining these
primitives. Table~\ref{tab:geant2fluka} lists the mapping between Geant4
solids and the bodies used to compose a FLUKA region.
\begin{figure}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
\caption{Example conversion of a simple GDML geometry to FLUKA, above:
the original model in \PYGEOMETRY{}, below: the converted FLUKA geometry
viewed in flair. The example is a sector bend dipole electromagnet.}
\label{fig:gdml-flair}
\end{center}
\end{figure}
